### 2016-05-19 plosOneJordanousKeller/rebuttal.txt

http://www.journals.plos.org/plosone/s/file?id=wjVg/PLOSOne_formatting_sample_main_body.pdf and http://www.journals.plos.org/plosone/s/file?id=ba62/PLOSOne_formatting_sample_title_authors_affiliations.pdf

***** For some reason, we've fallen foul of some of these, so I'll check that *****

1.  We request that you please report additional details in your Methods:
i) A detailed overview of the search strategy used to identify papers for the creativity corpus and non-creativity corpus
ii) The specific methods for selecting papers, including inclusion and exclusion criteria
In addition, please include a figure of a flow diagram describing your search strategy (see http://prisma-statement.org/PRISMAStatement/FlowDiagram.aspx for examples)
We appreciate your attention to these requests."

*****
* We have added, as requested, the detailed overview of our search strategy and the methods/criteria for selecting papers. This is reported in text added in the Methods section. Thank you for the link to the flow diagram examples.
***** PRISMA - ANNA TO DO THIS *****

@@

Literature Cited
Gabora, L., O’Connor, B., & Ranjan, A. (2012). The recognizability of individual creative styles within and across domains. Psychology of Aesthetics, Creativity, and the Arts, 6(4), 351-360.

 ***** ANNA TO CHECK HOW THE GABORA ET AL PAPER FITS INTO THIS
       (UNLESS THIS COMES UP IN THE WORK BILL IS DOING FOR REVIEWER 1'S MAIN POINT??) *****

A concern I have about the methodology concerns the set of papers used in the analysis, provided in Figure 1. (Note: this figure is rather hazy; in the final paper a higher resolution version should be used.) Despite the authors’ intention to capture how is creativity is understood from a broad range of vantage points and disciplines, almost all of these papers are in psychology journals. In my view they should have included papers from other scholarly journals that discuss creativity and innovation, e.g. design, architecture, art, theatre, film, multimedia, creative writing, electronic arts, and engineering journals.

 ***** 
 * We have edited the figure accordingly, thank you for this feedback. Regarding the raised concern: we have added a diagram representing the disciplinary makeup of the corpus, as categorised by the journal disciplinary classification in Scopus. Additionally, we have commented on the disciplinary coverage as part of the added text in the Methods section, which give a detailed report and discussion of our search strategy and methods for compiling the corpus. 
 *****

### 2016-05-19 plosOneJordanousKeller/PAPER/plos_JordanousKeller.tex
edits to add specific detail on search strategy and inclusion/exclusion criteria.

A sample of academic papers discussing the nature of creativity was assembled. This {\em creativity corpus\/} consisted of 30 papers examining creativity from various academic stand-points ranging from psychological studies to computational models.

@@

The 30 papers selected for the creativity corpus are listed in Fig. 1. %\ref{S1_Fig}.

i) A detailed overview of the search strategy used to identify papers for the creativity corpus and non-creativity corpus
ii) The specific methods for selecting papers, including inclusion and exclusion criteria

\textbf{Paper selection for the creativity corpus was governed by inclusion criteria based on measuring the influence of a paper and coverage of a wide range of years and academic disciplines: }
\begin{itemize}
\item \textbf{Papers must have, as their primary focus, discussion of the nature of creativity.}
\item \textbf{The primary inclusion criterion was to choose particularly influential papers, as measured by the number of times it had been cited by other academic authors. For papers published in recent years and which have consequently not yet accrued many citations, selection was based on subjective judgement of influence.}
\item \textbf{Cross section of years [the corpus was compiled in 2010] over the range of years 1950-2009. 1950 was chosen as a starting point in recognition of the effect of J. P. Guilford's presidential address to the American Psychological Association \cite{guilford50}, which examined contemporary creativity research (or more specifically, the lack of thereof). His talk was highly influential in encouraging more creativity research activity \cite{kaufman09}.}
\end{itemize}
\sout{The papers were carefully chosen so as to cover a wide range of years (1950-2009) and academic disciplines. A paper was included if it was considered particularly influential, as measured by the number of times it had been cited by other academic authors. For papers published in recent years and which have consequently not yet accrued many citations, selection was based on subjective judgement of influence.}

@@

Our objective is to identify what is distinctive in the language used to discuss creativity, in contrast to the language used to discuss other topics. As a basis for comparison, therefore, a further sample of 60 academic papers on topics unrelated to creativity -- the {\em non-creativity corpus} -- was assembled.

@@

The non-creativity corpus papers were selected by a literature search retrieving, for each paper in the creativity corpus, the two most-cited papers in the same academic discipline\footnote{As categorised by the literature database {\em Scopus} \texttt{http://www.scopus.com/})} published in the same year, that did not contain any words with the prefix {\em creat\/} (i.e. {\em creativity\/}, {\em creative\/}, {\em creation\/}, and so on).

@@

>>>>

A sample of academic papers discussing the nature of creativity was assembled as a {\em creativity corpus\/} in 2010. This creativity corpus consisted of 30 papers examining creativity from various academic stand-points ranging from psychological studies to computational models.

@@

The 30 papers selected for the creativity corpus are listed in Fig. 1a. %\ref{S1a_Fig}.

%**** i) A detailed overview of the search strategy used to identify papers for the creativity corpus and non-creativity corpus ****
%**** ii) The specific methods for selecting papers, including inclusion and exclusion criteria ****

\textbf{The search strategy for identifying papers for the corpus was based around a literature search for the term `creativity' on the academic database {\em Scopus}. Paper selection for the creativity corpus was governed by inclusion criteria based on measuring the influence of a paper and coverage of a wide range of years and academic disciplines. The inclusion criteria are as follows, listed in descending order of precedence: }
\begin{itemize}
\item \textbf{Papers must have, as their primary focus, discussion of the nature of creativity.}
\item \textbf{Papers should be considered particularly influential, as measured by the number of times it had been cited by other academic authors. For papers published in recent years and which have consequently not yet accrued many citations, selection was based on our subjective judgement of influence.}
\item \textbf{Papers selected should, as far as reasonable, represent a cross-section of years over the range 1950-2009. [The corpus was compiled in 2010.] 1950 was chosen as a starting point in recognition of the effect of J. P. Guilford's presidential address to the American Psychological Association \cite{guilford50}, which examined contemporary creativity research (or more specifically, the lack of thereof). His talk was highly influential in encouraging more creativity research activity \cite{kaufman09}. }
\item \textbf{Papers selected should, as far as reasonable, represent a cross-section of disciplines relevant to discussions of what creativity is. Fig. 1b. illustrates the disciplinary distribution of the corpus as it changes over the time period included in the corpus, according to journal disciplinary classification in the academic database {\em Scopus}, which classifies journals under their main subject area(s) covered. We should acknowledge here though that while many disciplines include work that applies information about creativity, often the focus is on application rather than in depth discussion of what creativity entails. Hence, while we sought to cover creativity from a broad range of perspectives, we also felt it was important not to compromise the key focus of our corpus as a representation of key discussions about the nature of creativity.}
\end{itemize}
\sout{The papers were carefully chosen so as to cover a wide range of years (1950-2009) and academic disciplines. A paper was included if it was considered particularly influential, as measured by the number of times it had been cited by other academic authors. For papers published in recent years and which have consequently not yet accrued many citations, selection was based on subjective judgement of influence.}

\textbf{Exclusion criteria for this search were: }
\begin{itemize}
\item \textbf{Authors were only represented more than one in the corpus if the relevant papers were written from different perspectives. For example, Mark Runco's work is represented twice in the corpus, but covering two different topics relating to the nature of creativity (psychoeconomic approach to creativity; cognition and creativity). If the search process highlighted two or more papers with a shared author, on the same or highly similar perspectives on creativity, then the more highly cited paper was chosen. }
\item \textbf{Papers had to be written in English, as the language processing tools we were working with were for English language texts.}
\item \textbf{Papers had to be available in a format that plain text could be extracted from (this excluded books or book chapters).}
\end{itemize}

@@

Our objective is to identify what is distinctive in the language used to discuss creativity, in contrast to the language used to discuss other topics. As a basis for comparison, therefore, a further sample of 60 academic papers on topics unrelated to creativity -- the {\em non-creativity corpus} -- was assembled \textbf{alongside the creativity corpus, in 2010}.

@@

The non-creativity corpus papers were selected by a literature search retrieving, for each paper in the creativity corpus, the two most-cited papers in the same academic discipline\footnote{As categorised by the literature database {\em Scopus} \texttt{http://www.scopus.com/})} published in the same year, that did not contain any words with the prefix {\em creat\/} (i.e. {\em creativity\/}, {\em creative\/}, {\em creation\/}, and so on). \textbf{In other words, inclusion for this second corpus was based on the criteria of if a paper was one of the two papers that was most highly cited at the time of the search (2010), in the same academic discipline, and published in the same year, as a paper in the creativity corpus (as determined by {\em Scopus}), and that satisfied the exclusion criteria of not containing any words with the above mentioned prefixes.}

@@

\textbf{Some pre-processing was undertaken for each paper in both the creativity corpus and non-creativity corpus prior to analysis. A plain text file was generated for each paper, containing the full text of that paper. All journal headers and copyright notices were removed from each paper, as were the author names and affiliations, list of references and acknowledgements. All files were also checked for any non-ascii characters and anomalies that may have arisen during the creation of the text file.}
